Universal Anonymous Signatures

### 2022-08-05 prism-backend/research/gsac/app-building-blocks.tex
Updating proofs.

\begin{figure}[ht!]
  \begin{minipage}[t]{\textwidth}
    \centering
    \procedure{$\ExpEUF(\Ssecpar)$}{%
      \Sparm \gets \SSetup(\Ssecpar) \\
      (\Svk,\Ssk) \gets \SKeyGen(\Sparm) \\
      (\Ssig,\msg) \gets \adv^{\SSign(\Ssk,\cdot)}(\Svk) \\
      \pcif \SVerify(\Svk,\Ssig,\msg) = 0: \pcreturn 0 \\
      \pcif \msg~\textrm{was not queried to \SSign}: \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \label{fig:euf-game}
  \caption{Existential Unforgeability Game.}
\end{figure}

@@

\begin{figure}[ht!]
  \begin{minipage}[t]{\textwidth}
    \centering      
    \procedure{$\ExpINDCCAiib(\Esecpar)$}{%
      \Eparm \gets \ESetup(\Esecpar) \\
      (\Eek,\Edk) \gets \EKeyGen(\Eparm) \\
      b^* \gets \adv^{\ELR(b,\cdot,\cdot),\EDEC(\Edk,\cdot)}(\Eek),
      ~\textrm{where:} \\
      \pcind \ELR(b,\msg_0,\msg_1)~\textrm{returns}~\EEnc(\Eek,\msg_b),
      ~\textrm{and} \\
      \pcind \EDEC(\Edk,\Ec)~\textrm{returns}~\EDec(\Edk,\Ec) \\
      \pcif \EDEC~\textrm{has been called with an output of \ELR, abort} \\
      \pcreturn b^*
    }
  \end{minipage}
  \label{fig:indcca2-game}
  \caption{IND-CCA2 Game.}
\end{figure}

@@

\begin{figure}[ht!]
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpComBind(\Csecpar)$}{%
      \Cparm \gets \CSetup(\Csecpar) \\
      (\msg_0,r_0,\msg_1,r_1) \gets \adv(\Cparm) \\
      \Ccom_0 \gets \CCommit(\Cparm,\msg_0,r_0) \\
      \Ccom_1 \gets \CCommit(\Cparm,\msg_1,r_1) \\
      \pcif \msg_0 \neq \msg_1 \land \Ccom_0 = \Ccom_1: \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpComHideb(\secpar)$}{%
      \Cparm \gets \CSetup(\secpar) \\
      b' \gets \adv^{COM(\Cparm,\cdot,\cdot)},~\textrm{where}: \\
      \pcind COM(\Cparm,\msg_0,\msg_1): \\
      \pcind \pcind r \getr \mathcal{R};~\pcreturn \CCommit(\Cparm,\msg_b,r) \\
      % (\msg_0,\msg_1,st) \gets \adv(\Cparm) \\
      % r \getr \mathcal{R} \\
      % \Ccom \gets \CCommit(\Cparm,\msg_b,r) \\
%      b' \gets \adv(st,\Ccom) \\
      \pcreturn b'
    }
  \end{minipage}
  \label{fig:com-games}
  \caption{Games for commitment schemes.}
\end{figure}

@@

\begin{figure}[ht!]
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpNIZKComp(\NIZKsecpar)$}{%
      \NIZKcrs \gets \Setup(\NIZKsecpar) \\
      (\NIZKx,\NIZKw) \gets \adv(\NIZKcrs) \\
      \pcif (\NIZKx,\NIZKw) \notin \NIZKRel: \pcreturn 0 \\
      \NIZKproof \gets \Prove(\NIZKcrs,\NIZKx,\NIZKw) \\
      b \gets \Verify(\NIZKcrs,\NIZKproof,\NIZKx) \\
      \pcreturn b \\
    }
    \procedure{$\ExpNIZKSimExt(\NIZKsecpar)$}{%
      (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\NIZKsecpar) \\
      (\NIZKx,\NIZKproof) \gets \adv^{\Sim'(\NIZKcrs,\NIZKtrap,\cdot,\cdot)}
      (\NIZKcrs) \\
      \pcind \textrm{Where}~\Sim'(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKw)~\textrm{returns} \\
      \pcind \pcind
      \Sim(\NIZKcrs,\NIZKtrap,\NIZKx)~\pcif (\NIZKx,\NIZKw) \in \NIZKRel \\
      \pcind \pcind \bot~\pcif (\NIZKx,\NIZKw) \notin \NIZKRel \\
      \NIZKw' \gets \Extract(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKproof) \\
      \pcif \Verify(\NIZKcrs,\NIZKproof,\NIZKx) = 1 \land
      (\NIZKx,\NIZKw') \notin \NIZKRel~\land \\
      \pcind \NIZKx~\textrm{was not queried to $\Sim$ via $\Sim'$}: \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }    
  \end{minipage}
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpNIZKSound(\NIZKsecpar)$}{%
      \NIZKcrs \gets \Setup(\NIZKsecpar) \\
      (\NIZKproof,\NIZKx) \gets \adv(\NIZKcrs) \\
      \pcif \NIZKx \notin \NIZKLang \land
      \Verify(\NIZKcrs,\NIZKproof,\NIZKx): \\
      \pcind \pcreturn 0 \\
      \pcreturn 1 \\
    }

    \procedure{$\ExpNIZKZKb(\NIZKsecpar)$}{%
      \pcif b = 0: \\
      \pcind \NIZKcrs \gets \Setup(\NIZKsecpar) \\
      \pcind \pcreturn \adv^{\Prove(\NIZKcrs,\cdot,\cdot)}(\NIZKcrs) \\
      \pcif b = 1: \\
      \pcind (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\secpar) \\
      \pcind \pcreturn \adv^{\Sim'(\NIZKcrs,\NIZKtrap,\cdot,\cdot)}(\NIZKcrs),~
      \textrm{where} \\
      \pcind \Sim'(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKw)~\textrm{returns} \\
      \pcind \pcind \Sim(\NIZKcrs,\NIZKtrap,\NIZKx)~\pcif (\NIZKx,\NIZKw)
      \in \NIZKRel \\
      \pcind \pcind \bot~\pcif (\NIZKx,\NIZKw) \notin \NIZKRel
    }    
  \end{minipage}
  \label{fig:nizk-games}
  \caption{Games for Simulation-Extractable NIZK schemes.}
\end{figure}

@@

\begin{figure}[ht!]
  \begin{minipage}[t]{\textwidth}
    \centering    
    \procedure{$\ExpSBMEUF(\SBMsecpar)$}{%
      \SBMparm \gets \SBMSetup(\SBMsecpar) \\
      (\SBMvk,\SBMsk) \gets \SBMKeyGen(\SBMparm) \\
      (\SBMsig,\smsg) \gets \adv^{\SSign(\SBMsk,\cdot)}(\SBMvk) \\
      \pcif \SBMVerify(\SBMvk,\SBMsig,\smsg) = 0: \pcreturn 0 \\
      \pcif \smsg~\textrm{was not queried to \SBMSign}: \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \label{fig:sbm-games}
  \caption{Unforgeability game for \SBM schemes.}
\end{figure}
\fi

@@

\begin{figure}[ht!]
  \begin{minipage}[t]{\textwidth}
    \centering

@@

    \procedure[linenumbering]{$\ExpSBCMBlindb(\SBCMsecpar)$}{%
      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
      (\overline{\smsg}_0,\overline{\smsg}_1,\smsg) \gets
      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
      \csig \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg}_b,\smsg),
      \SBCMSign(\SBCMsk,\smsg) \rangle \\
      b^* \gets \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk,
      \csig) \\
      \pcif b = b^*: \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \label{fig:sbcm-games}
  \caption{Games for \SBCM schemes.}
\end{figure}

\paragraph{Augmenting with NIZKs.} %
\todo{This is quite informal. Perhaps expand...} 
In the previous \SBCM scheme, it is straightforward to require that the party
running \SBCMCom proves, in zero knowledge, some arbitrary claim over the
messages to be signed (both those in committed or plaintext form), as well as
over possibly extra auxiliary data. This can be done by having this party add a
NIZK over the corresponding NP statement, which has later to be verified by the
party running \SBCMSign.
%
Clearly, if the base \SBCM scheme satisfies blindness, then extending it with a
zero-knowledge NIZK proof over the (blindly) signed messages, still maintains
blindness (the adversary cannot distinguish which committed messages set is
signed, in the blindness game).
%
We use this extension in our \CUASGen construction, and thus extend the previous
syntax for interactive signing  as follows, to account for an extra NIZK
relation \NIZKRel proving that a pair of statement $x$ and witness $w$ belong
\NIZKRel.

>>>>

\begin{figure}[ht!]
  \scalebox{0.9}{  
    \begin{minipage}[t]{\textwidth}
      \centering
      \procedure{$\ExpEUF(\Ssecpar)$}{%
        \Sparm \gets \SSetup(\Ssecpar) \\
        (\Svk,\Ssk) \gets \SKeyGen(\Sparm) \\
        (\Ssig,\msg) \gets \adv^{\SSign(\Ssk,\cdot)}(\Svk) \\
        \pcif \SVerify(\Svk,\Ssig,\msg) = 0: \pcreturn 0 \\
        \pcif \msg~\textrm{was not queried to \SSign}: \pcreturn 1 \\
        \pcreturn 0
      }
    \end{minipage}
  }
  \label{fig:euf-game}
  \caption{Existential Unforgeability Game.}
\end{figure}

@@

\begin{figure}[ht!]
  \scalebox{0.9}{  
    \begin{minipage}[t]{\textwidth}
      \centering      
      \procedure{$\ExpINDCCAiib(\Esecpar)$}{%
        \Eparm \gets \ESetup(\Esecpar) \\
        (\Eek,\Edk) \gets \EKeyGen(\Eparm) \\
        b^* \gets \adv^{\ELR(b,\cdot,\cdot),\EDEC(\Edk,\cdot)}(\Eek),
        ~\textrm{where:} \\
        \pcind \ELR(b,\msg_0,\msg_1)~\textrm{returns}~\EEnc(\Eek,\msg_b),
        ~\textrm{and} \\
        \pcind \EDEC(\Edk,\Ec)~\textrm{returns}~\EDec(\Edk,\Ec) \\
        \pcif \EDEC~\textrm{has been called with an output of \ELR, abort} \\
        \pcreturn b^*
      }
    \end{minipage}
  }
  \label{fig:indcca2-game}
  \caption{IND-CCA2 Game.}
\end{figure}

@@

\begin{figure}[ht!]
  \scalebox{0.9}{
    \begin{minipage}[t]{0.5\textwidth}
      \procedure{$\ExpComBind(\Csecpar)$}{%
        \Cparm \gets \CSetup(\Csecpar) \\
        (\msg_0,r_0,\msg_1,r_1) \gets \adv(\Cparm) \\
        \Ccom_0 \gets \CCommit(\Cparm,\msg_0,r_0) \\
        \Ccom_1 \gets \CCommit(\Cparm,\msg_1,r_1) \\
        \pcif \msg_0 \neq \msg_1 \land \Ccom_0 = \Ccom_1: \pcreturn 1 \\
        \pcreturn 0
      }
    \end{minipage}
    \begin{minipage}[t]{0.5\textwidth}
      \procedure{$\ExpComHideb(\secpar)$}{%
        \Cparm \gets \CSetup(\secpar) \\
        b' \gets \adv^{COM(\Cparm,\cdot,\cdot)},~\textrm{where}: \\
        \pcind COM(\Cparm,\msg_0,\msg_1): \\
        \pcind \pcind r \getr \mathcal{R};~\pcreturn \CCommit(\Cparm,\msg_b,r) \\
        % (\msg_0,\msg_1,st) \gets \adv(\Cparm) \\
        % r \getr \mathcal{R} \\
        % \Ccom \gets \CCommit(\Cparm,\msg_b,r) \\
        % b' \gets \adv(st,\Ccom) \\
        \pcreturn b'
      }
    \end{minipage}
  }
  \label{fig:com-games}
  \caption{Games for commitment schemes.}
\end{figure}

@@

\begin{figure}[ht!]
  \scalebox{0.9}{
    \begin{minipage}[t]{0.5\textwidth}
      \procedure{$\ExpNIZKComp(\NIZKsecpar)$}{%
        \NIZKcrs \gets \Setup(\NIZKsecpar) \\
        (\NIZKx,\NIZKw) \gets \adv(\NIZKcrs) \\
        \pcif (\NIZKx,\NIZKw) \notin \NIZKRel: \pcreturn 0 \\
        \NIZKproof \gets \Prove(\NIZKcrs,\NIZKx,\NIZKw) \\
        b \gets \Verify(\NIZKcrs,\NIZKproof,\NIZKx) \\
        \pcreturn b \\
      }
      \procedure{$\ExpNIZKSimExt(\NIZKsecpar)$}{%
        (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\NIZKsecpar) \\
        (\NIZKx,\NIZKproof) \gets \adv^{\Sim'(\NIZKcrs,\NIZKtrap,\cdot,\cdot)}
        (\NIZKcrs) \\
        \pcind \textrm{Where}~\Sim'(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKw)~\textrm{returns} \\
        \pcind \pcind
        \Sim(\NIZKcrs,\NIZKtrap,\NIZKx)~\pcif (\NIZKx,\NIZKw) \in \NIZKRel \\
        \pcind \pcind \bot~\pcif (\NIZKx,\NIZKw) \notin \NIZKRel \\
        \NIZKw' \gets \Extract(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKproof) \\
        \pcif \Verify(\NIZKcrs,\NIZKproof,\NIZKx) = 1 \land
        (\NIZKx,\NIZKw') \notin \NIZKRel~\land \\
        \pcind \NIZKx~\textrm{was not queried to $\Sim$ via $\Sim'$}: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }    
    \end{minipage}
    \begin{minipage}[t]{0.5\textwidth}
      \procedure{$\ExpNIZKSound(\NIZKsecpar)$}{%
        \NIZKcrs \gets \Setup(\NIZKsecpar) \\
        (\NIZKproof,\NIZKx) \gets \adv(\NIZKcrs) \\
        \pcif \NIZKx \notin \NIZKLang \land
        \Verify(\NIZKcrs,\NIZKproof,\NIZKx): \\
        \pcind \pcreturn 0 \\
        \pcreturn 1 \\
      }

      \procedure{$\ExpNIZKZKb(\NIZKsecpar)$}{%
        \pcif b = 0: \\
        \pcind \NIZKcrs \gets \Setup(\NIZKsecpar) \\
        \pcind \pcreturn \adv^{\Prove(\NIZKcrs,\cdot,\cdot)}(\NIZKcrs) \\
        \pcif b = 1: \\
        \pcind (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\secpar) \\
        \pcind \pcreturn \adv^{\Sim'(\NIZKcrs,\NIZKtrap,\cdot,\cdot)}(\NIZKcrs),~
        \textrm{where} \\
        \pcind \Sim'(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKw)~\textrm{returns} \\
        \pcind \pcind \Sim(\NIZKcrs,\NIZKtrap,\NIZKx)~\pcif (\NIZKx,\NIZKw)
        \in \NIZKRel \\
        \pcind \pcind \bot~\pcif (\NIZKx,\NIZKw) \notin \NIZKRel
      }    
    \end{minipage}
  }
  \label{fig:nizk-games}
  \caption{Games for Simulation-Extractable NIZK schemes.}
\end{figure}

@@

\begin{figure}[ht!]
  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \centering    
      \procedure{$\ExpSBMEUF(\SBMsecpar)$}{%
        \SBMparm \gets \SBMSetup(\SBMsecpar) \\
        (\SBMvk,\SBMsk) \gets \SBMKeyGen(\SBMparm) \\
        (\SBMsig,\smsg) \gets \adv^{\SSign(\SBMsk,\cdot)}(\SBMvk) \\
        \pcif \SBMVerify(\SBMvk,\SBMsig,\smsg) = 0: \pcreturn 0 \\
        \pcif \smsg~\textrm{was not queried to \SBMSign}: \pcreturn 1 \\
        \pcreturn 0
      }
    \end{minipage}
  }
  \label{fig:sbm-games}
  \caption{Unforgeability game for \SBM schemes.}
\end{figure}
\fi

@@

\begin{figure}[ht!]
  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \centering

@@

      \procedure[linenumbering]{$\ExpSBCMBlindb(\SBCMsecpar)$}{%
        \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
        (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
        % (\st,\overline{\smsg}_0,\overline{\smsg}_1,\smsg) \gets
        % \adv(\SBCMvk,\SBCMsk) \\
        b^* \gets %\langle \SBCMCom(\SBCMvk,\overline{\smsg}_b,\smsg),
        \adv^{\langle COM(\SBCMvk,\overline{\smsg}_{\bin},\smsg),\cdot\rangle}(\SBCMsk) \\
        \pcreturn b = b^*
      }
    \end{minipage}
  }
  \label{fig:sbcm-games}
  \caption{Games for \SBCM schemes. The $COM$ oracle in \ExpSBCMBlindb receives
    $\overline{\smsg}_0$ and $\overline{\smsg}_1$, and runs a $\langle
    \SBCMCom(\SBCMvk,\overline{\smsg}_b,\smsg),\cdot\rangle$ protocol with the
    adversary acting as signer.}
\end{figure}

\paragraph{Augmenting with NIZKs.} %
\todo{This is quite informal. Perhaps expand...} 
In the previous \SBCM scheme, it is straightforward to require that the party
running \SBCMCom proves, in zero knowledge, some arbitrary claim over the
messages to be signed (both those in committed or plaintext form), as well as
over possibly extra auxiliary data. This can be done by having this party add a
NIZK over the corresponding NP statement, which has later to be verified by the
party running \SBCMSign.
%
If the base \SBCM scheme satisfies blindness, then extending it with a
zero-knowledge NIZK proof over the (blindly) signed messages, still maintains
blindness (the adversary cannot distinguish which committed message set is
signed, in the blindness game).
%
We use this extension in our \CUASGen construction, and thus extend the previous
syntax for interactive signing  as follows, to account for an extra NIZK
relation \NIZKRel proving that a pair of statement $x$ and witness $w$ belong
\NIZKRel.
